Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
abstract: mkl's proposition

>>>>

\emph{mkl proposes:}
When wading through the numerous libraries written by
the Haskell community, one sometimes gets the impression that the type
system is being too much relied on, at the expense of testing.
While the type system cannot always guarantee semantic correctness,
test code has more applications than getting the code correct.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
QuickCheck integrated in Doctest for user documentation and Hspec
with new mnemonic combinators for code documentation.
Our method utilizes specification that can also be used for
documentation and automatic testing. We hope that this three-in-one
quality motivates Haskellers to write more test code.
